The value of being indispensable: a cooperative approach to bargaining with a continuum of players

### 2024-02-29 src/paper/theory.tex
Streamline abstract

\begin{abstract}
    This paper investigates the idea of using concepts random order values, a concept from cooperative game theory, to model bargaining outcomes in games with an indispensable player and a continuum of fringe players.
    I show that this approach proves to be very tractable in a number of settings, and leads to results that are in line with one's intuitive expectations about bargaining outcomes.
    Thus, it can be a useful tool in modelling situations where one does not want to attribute all the bargaining power to one type of market participants, and at the same time would like to avoid having to deal with an explicit multi-stage bargaining game.
    On one hand, this paper provides a taxonomy of the various results found in some applied papers.
    Furthermore, it introduces some new results pertaining to the case of multiple types of fringe players.
    The utility of this approach is demonstrated via a simple model of two-sided markets.
    The results in this paper are intended to be used as a tool-kit for embedding bargaining outcomes into more complex models.
\end{abstract}

>>>>

\begin{abstract}
    This paper investigates the idea of using random order values, a concept from cooperative game theory, to model bargaining outcomes in games with one indispensable player and a continuum of fringe players.
    Two important special cases of random order values are discussed in detail: the Shapley value and the weighted value.
    I show that this approach proves to be very tractable, and leads to results that are in line with one's intuitive expectations about bargaining outcomes.
    Thus, it can be a useful tool in modelling situations where one does not want to attribute all the bargaining power to one side of the market, and at the same time would like to avoid having to deal with an explicit multi-stage bargaining game.
    The utility of this approach is demonstrated via a simple model of a two-sided market.
\end{abstract}
